Untitled

### 2022-12-10 draft_report.Rmd
modularized scripts

root <- dirname(getSourceEditorContext()$path)
source(paste0(root,"/input_data_prep_functions.R"))

#source(paste0(root,"/haplotype_reconstruction_pipelines.R"))

@@

```{r}
# simulated phenotypes
list_pheno <- c('WBC', 'NEUT')
```

@@

```{r}
do_results <- haplotype_reconstruction_pipeline('DO', list_pheno, qtl2_file_gen = F, samples_gen = F, truth_model = F)

@@

ind_gm <- summary_df[summary_df$`Haplotype Candidate` == 'False',]$`ID`
ind_gm <- ind_gm[!ind_gm %in% ind_gm[1:44]] # founder not in UWisc dictionary (SJL)
ind_gm <- ind_gm[!ind_gm %in% ind_gm[4:24]] # empty - Q2-QP
ind_gm <- ind_gm[!ind_gm %in% c('QU', 'SM', 'SX', 'T5', 'TG', 'TR', 'TS', 'TX', 'UF', 'UR', 'VA', 'VE', 'VG', 'VK', 'VN', 'W4', 'XS', 'Y8', 'Z8', 'ZG')] # screentime error
ind_gm <- ind_gm[!ind_gm %in% c('RY', 'S8', 'SG', 'SR', 'Y2', 'YA', 'YJ', 'YT')] # only one founder
ind_gm <- ind_gm[!ind_gm %in% c('U2', 'UA', 'UJ' ,'UT', 'W5', 'WD', 'WN', 'XZ', 'Y9', 'YH', 'YS')] # SJL 
ind_gm <- ind_gm[!ind_gm %in% c('UK', 'UU', 'V4')] #C57BLKS/J
ind_gm <- ind_gm[!ind_gm %in% c('WX', 'X7', 'X8', 'XF', 'XG', 'XQ', 'XR', 'XY', 'YG', 'YR')] # 129P3
ind_gm <- ind_gm[!ind_gm %in% c('WY')] # FVB/NJ
ind_gm <- ind_gm[!ind_gm %in% c('X2', 'X3', 'X4', 'X5', 'XA', 'XB', 'XC', 'XD', 'XJ', 'XK', 'XM', 'XN', 'XT', 'XU', 'XV', 'XW', 'Y2', 'Y3', 'Y4', 'Y5', 'YB', 'YC', 'YD', 'YE', 'YK', 'YM', 'YN', 'YP', 'YU', 'YV', 'YW', 'YX', 'Z5', 'Z6', 'Z7', 'ZC', 'ZD', 'ZE', 'ZF', 'ZM', 'ZN', 'ZP', 'ZQ', 'ZV', 'ZW', 'ZX', 'ZY', 'PY', 'Z3', 'ZB' ,'ZK', 'ZU')] # empty ones

gigamuga_results <- list()
gm_pct_res <- list()
for (ind in ind_gm) {
  print(ind)
  sample_gm_res <- sample_haplotype_reconstruction('MURGIGV01', ind, samples_gen = T, qtl2_file_gen = T)
  df <- minimuga_geno_comp(gigamuga_results[[ind]], ind, 'MURGIGV01')

@@

```{r}
### MiniMUGA pipeline
minimuga_url <- 'http://haploqa-dev.jax.org/tag/MiniMUGA.html'
url_domain <- 'http://haploqa-dev.jax.org/'
marker_type <- 'MiniMUGA'
html_table <- read_html(minimuga_url) %>% html_nodes("a") %>% html_attr("href")
url_list <- paste0(url_domain, html_table[grepl('/sample', html_table)])
summary_df <- sample_summary_scrape(read_html(minimuga_url), url_list, marker_type)
ind_mini <- summary_df[summary_df$`Haplotype Candidate` == 'False',]$`ID`
ind_mini <- ind_mini[ind_mini!='JXX'] # screentime error, skip this one
ind_mini <- ind_mini[ind_mini!='JY9'] # only 1 contributing strain, AIL incompatible, skip this one as well
ind_mini <- ind_mini[ind_mini!='JY6'] # temporary - JXU, JY3, JY5
minimuga_results <- list()
mini_pct_res <- list()
for (ind in ind_mini) {
  #ind <- 'JXN'
  print(ind)
  sample_mini_res <- sample_haplotype_reconstruction('MiniMUGA', ind, samples_gen = F, qtl2_file_gen = F)
  df <- minimuga_geno_comp(sample_mini_res, ind, 'MiniMUGA')

@@

@@

@@

@@

>>>>

root <- dirname(getSourceEditorContext()$path)
#source(paste0(root,"/input_data_prep_functions.R"))

source(paste0(root,"/haplotype_reconstruction_pipelines.R"))

# simulated phenotypes
list_pheno <- c('WBC', 'NEUT')
```

@@

@@

```{r}
do_results <- haplotype_reconstruction_pipeline('DO', list_pheno, qtl2_file_gen = F, samples_gen = F)

@@

ind_gm <- summary_df[summary_df$`Haplotype Candidate` == 'False',]$`ID`
#ind_gm <- ind_gm[!ind_gm %in% ind_gm[1:44]] # founder not in UWisc dictionary (SJL)
#ind_gm <- ind_gm[!ind_gm %in% ind_gm[4:24]] # empty - Q2-QP
ind_gm <- ind_gm[!ind_gm %in% c('QU', 'SM', 'SX', 'T5', 'TG', 'TR', 'TS', 'TX', 'UF', 'UR', 'VA', 'VE', 'VG', 'VK', 'VN', 'W4', 'XS', 'Y8', 'Z8', 'ZG')] # screentime error
ind_gm <- ind_gm[!ind_gm %in% c('RY', 'S8', 'SG', 'SR', 'Y2', 'YA', 'YJ', 'YT')] # only one founder
#ind_gm <- ind_gm[!ind_gm %in% c('U2', 'UA', 'UJ' ,'UT', 'W5', 'WD', 'WN', 'XZ', 'Y9', 'YH', 'YS')] # SJL 
#ind_gm <- ind_gm[!ind_gm %in% c('UK', 'UU', 'V4')] #C57BLKS/J
#ind_gm <- ind_gm[!ind_gm %in% c('WX', 'X7', 'X8', 'XF', 'XG', 'XQ', 'XR', 'XY', 'YG', 'YR')] # 129P3
#ind_gm <- ind_gm[!ind_gm %in% c('WY')] # FVB/NJ
#ind_gm <- ind_gm[!ind_gm %in% c('X2', 'X3', 'X4', 'X5', 'XA', 'XB', 'XC', 'XD', 'XJ', 'XK', 'XM', 'XN', 'XT', 'XU', 'XV', 'XW', 'Y2', 'Y3', 'Y4', 'Y5', 'YB', 'YC', 'YD', 'YE', 'YK', 'YM', 'YN', 'YP', 'YU', 'YV', 'YW', 'YX', 'Z5', 'Z6', 'Z7', 'ZC', 'ZD', 'ZE', 'ZF', 'ZM', 'ZN', 'ZP', 'ZQ', 'ZV', 'ZW', 'ZX', 'ZY', 'PY', 'Z3', 'ZB' ,'ZK', 'ZU')] # empty ones

gigamuga_results <- list()
gm_pct_res <- list()
for (ind in ind_gm) {
  print(ind)
  sample_gm_res <- sample_haplotype_reconstruction('MURGIGV01', ind, samples_gen = T, qtl2_file_gen = T)
  df <- ind_geno_comp(sample_gm_res, ind, 'MURGIGV01')

@@

```{r}
### MiniMUGA pipeline
minimuga_url <- 'http://haploqa-dev.jax.org/tag/MiniMUGA.html'
url_domain <- 'http://haploqa-dev.jax.org/'
marker_type <- 'MiniMUGA'
html_table <- read_html(minimuga_url) %>% html_nodes("a") %>% html_attr("href")
url_list <- paste0(url_domain, html_table[grepl('/sample', html_table)])
summary_df <- sample_summary_scrape(read_html(minimuga_url), url_list, marker_type)
ind_mini <- summary_df[summary_df$`Haplotype Candidate` == 'False',]$`ID`
ind_mini <- ind_mini[ind_mini!='JXX'] # screentime error, skip this one
ind_mini <- ind_mini[ind_mini!='JY9'] # only 1 contributing strain, AIL incompatible, skip this one as well
ind_mini <- ind_mini[ind_mini!='JY6'] # temporary - JXU, JY3, JY5
minimuga_results <- list()
mini_pct_res <- list()
for (ind in ind_mini) {
  #ind <- 'JXN'
  print(ind)
  sample_mini_res <- sample_haplotype_reconstruction('MiniMUGA', ind, samples_gen = F, qtl2_file_gen = F)
  df <- ind_geno_comp(sample_mini_res, ind, 'MiniMUGA')

@@

mini_pct_res <- rbindlist(mini_pct_res)
```

@@

(add screenshots of karyotype plots for outliers)

@@

(make a plot to visualize run time)
(talk about the strengths and weaknesses)
(figure out the error LOD)
qtl2 does not scale well with large number of founders

@@

qtl2fst - store large objects 
calc_genoprob_fst
(allele prob fst)
for DO - 
time the regular genoprob and fst
get the file size/memory usage of RDS and FST
